%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {\textbf{PhD in Neuroscience}} % Degree
    {University of Victoria} % Institution
    {Victoria, BC. Canada} % Location
    {Jan. 2015 - April. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item \textbf{Dissertation}: Pannexin 1 regulates dendritic spine formation.
        \item \textbf{GPA}: 8.2/9.0.
          \begin{itemize}
          \item \textbf{Relevant Coursework:} Developmental neurobiology, Tools for the study of ion channels.
          \end{itemize}   
      \end{cvitems}
    }
  
    \cventry
    {\textbf{Doctor of Medicine}} % Degree
    {Universidad del Valle - School of Medicine} % Institution
    {Cali, Valle. Colombia} % Location
    {Aug. 2007 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item \textbf{Pre-Diploma Rotatory Internship}: Hospital Universitario del Valle ESE - Universidad del Valle. Cali, Valle. Colombia.
        \item \textbf{Research Internship}: Centro de Estudios Cerebrales (Centre for Brain Studies). Universidad del Valle. Cali, Valle. Colombia
        \begin{itemize}
         \item \textit{Area of study}: Cerebral cortex cytoarchitectonics, functional neuronatomy, diffuse traumatic brain injury and ischemic stroke models in rats. Supervisors: Prof. Hernan Pimienta, Prof. Marhta Escobar, and Prof. Efrain Buritica.  
        \end{itemize}
        \item \textbf{Observership}: Functional Neurosurgery.  Department of Neurosurgery.  University of Illinois Hospital \& Health Sciences System. University of Illinois at Chicago. Chicago, IL. USA. Supervisor: Dr. Konstantin Slavin.
        \item \textbf{Professional elective}: Neurosurgery and Neurocritical Care. Department of Neurosurgery.Hospital Universitario del Valle ESE - Universidad del Valle. Cali, Valle. Colombia.
        \item \textbf{GPA}: 4.4/5.0.
          \begin{itemize}
          \item \textbf{Relevant Coursework:} Functional Neuroanatomy, Cerebral cortex cytoarchitectonics, Scientific Integrity, Bio-statistics, Addiction and Pharmacology, Systems Pathology
          \end{itemize}   
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
